### 2022-05-30 README.Rmd
update links to chris-prener

[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
[![CRAN_status_badge](https://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](https://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](https://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](https://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@

## Installation
### Installing Dependencies
You should check the [`sf` package website](https://r-spatial.github.io/sf/) and the [`areal` package website](https://slu-openGIS.github.io/areal/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system. For best results, have `sf` installed before you install `areal`. Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.

The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [special instructions](https://github.com/r-spatial/lwgeom) to install correctly.

### Installing areal
The easiest way to get `areal` is to install it from CRAN:

@@

```r
# install.packages("remotes")
remotes::install_github("slu-openGIS/areal")
```

@@

### Areal Weighted Interpolation
`areal` currently implements an approach to interpolation known as areal weighted interpolation. It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for details). The basic usage of `areal` is through the `aw_interpolate()` function. This is a pipe-able function that allows for the simultaneous interpolation of multiple values.

@@

This example outputs a simple features (`sf`) object and uses one of two options for calculating weights. All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://slu-opengis.github.io/areal/).

@@

Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Functions for validating data, previewing the areal weights, and walking step-by-step through the interpolation process are provided. See the [areal weighted interpolation vignette](https://slu-opengis.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.

@@

- [Pycnophylactic method](https://github.com/slu-openGIS/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
- [Binary dasymetric method](https://github.com/slu-openGIS/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
- [3-class regression dasymetric method](https://github.com/slu-openGIS/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)

@@

## Contributor Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](https://slu-opengis.github.io/areal/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.

>>>>

[![R build status](https://github.com/chris-prener/areal/workflows/R-CMD-check/badge.svg)](https://github.com/chris-prener/areal/actions)
[![Coverage status](https://codecov.io/gh/chris-prener/areal/branch/master/graph/badge.svg)](https://codecov.io/github/chris-prener/areal?branch=main)
[![CRAN_status_badge](https://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](https://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](https://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](https://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@

## Installation
The easiest way to get `areal` is to install it from CRAN:

@@

```r
# install.packages("remotes")
remotes::install_github("chris-prener/areal")
```

Note that installations that require `sf` to be built from *source* will require additional software regardless of operating system. You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system.

@@

### Areal Weighted Interpolation
`areal` currently implements an approach to interpolation known as areal weighted interpolation. It is arguably the simplest and most common approach to areal interpolation, though it does have some drawbacks (see the [areal weighted interpolation vignette](https://chris-prener.github.io/areal/articles/areal-weighted-interpolation.html) for details). The basic usage of `areal` is through the `aw_interpolate()` function. This is a pipe-able function that allows for the simultaneous interpolation of multiple values.

@@

This example outputs a simple features (`sf`) object and uses one of two options for calculating weights. All of these arguments are documented both within the package (use `?aw_interpolate`) and on the [package's website](https://chris-prener.github.io/areal/).

@@

Another advantage of `areal` is that the interpolation process is not a "black box", but rather can be manually completed if necessary. Functions for validating data, previewing the areal weights, and walking step-by-step through the interpolation process are provided. See the [areal weighted interpolation vignette](https://chris-prener.github.io/areal/articles/areal-weighted-interpolation.html) for additional details about this workflow.

@@

- [Pycnophylactic method](https://github.com/chris-prener/areal/issues/1) (raster based, eliminates the sharp transitions in value between target features)
- [Binary dasymetric method](https://github.com/chris-prener/areal/issues/2) (incorporates ancillary data so that population is not assumed to be evenly distributed within units)
- [3-class regression dasymetric method](https://github.com/chris-prener/areal/issues/3) (allows for a more complex estimation based on multiple forms of ancillary data)

@@

## Contributor Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](https://chris-prener.github.io/areal/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
